Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-05 doc/paper.tex
work on Computational section

	\section{Computational Results}
	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
	\begin{itemize}
		\item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}
     We used three different kind of benchmarks:
     \begin{itemize}
     	\item \emph{random} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     	\item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	\item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
	\subsection{Results on exact methods}
\fxnote{Marko: Solving of CP i MIP solvers are limited to 5 mins. }
	\section{Conclusions and Future Work}

>>>>

	\section{Computational Results}
	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
	\begin{itemize}
		\item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}
     We used three different kind of benchmark sets:
     \begin{itemize}
     	\item \emph{random} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     	\item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	\item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     Fro small and large instances, one polygon with $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set. For random set, we took a subset of 200 instances. In overall, we have 400 polygons which vertices are weighted by two different weights, which gives us, in overall, 800 instances.
	\subsection{Results on exact methods}
\fxnote{Marko: Solving of CP i MIP solvers are limited to 5 mins. }
	\section{Conclusions and Future Work}
